
\documentclass{article}
\usepackage{amsmath}
\begin{document}
### Northwestern University
### Advanced Level Examination
#### Subject: Undefined
##### Difficulty Level: 7 (Out of 10)
##### Date: [Insert Date]
##### Time: [Insert Time]

---

**Instructions:**

1. Answer all questions in the spaces provided.
2. Be clear and concise in your responses.
3. Show all your workings where applicable.
4. Calculators are allowed but must not have internet access.
5. This test is 2 hours long. Manage your time wisely.

---

**Section A: Analytical Reasoning and Problem Solving**

**Question 1: Critical Analysis**  
*(20 Points)*

Consider the following scenario: A new policy in a multinational corporation intends to redistribute resources more equitably across its departments. This change faces resistance from middle management due to perceived biases and potential loss of control. Analyze both the benefits and the drawbacks of such a policy. Propose a method to mitigate resistance and facilitate smoother implementation.

---

**Question 2: Data Interpretation**  
*(15 Points)*

The following data gives the yearly revenue (in millions) of a company over the past five years:

| Year | Revenue (in millions USD) |
|------|---------------------------|
| 2018 | 45.3                      |
| 2019 | 50.8                      |
| 2020 | 47.2                      |
| 2021 | 53.5                      |
| 2022 | 58.1                      |

- Plot the data on a graph.
- Calculate the average annual growth rate.
- Interpret the trend shown by the data and provide possible reasons for any anomalies.

---

**Section B: Quantitative Analysis**

**Question 3: Calculus Application**  
*(15 Points)*

Find the local maxima, minima, and points of inflection of the function f(x) = 3x^3 - 12x^2 + 8x + 1. Justify your answer using the first and second derivative tests.

---

**Question 4: Probability and Statistics**  
*(10 Points)*

A factory produces light bulbs, and it is known that 2% of the bulbs are defective. If a quality control team randomly selects 15 bulbs from the production line, what is the probability that exactly 1 bulb is defective? Provide your solution using the binomial probability formula.

---

**Section C: Theoretical Concepts**

**Question 5: Philosophy**  
*(10 Points)*

Discuss the concept of "Tabula Rasa" as introduced by John Locke. How does this concept contrast with the nativist perspective in the nature vs. nurture debate? Provide examples to support your analysis.

---

**Question 6: Ethics**  
*(10 Points)*

Examine the ethical implications of whistle-blowing in a corporate environment. Discuss the potential benefits and risks for the whistle-blower and the organization. Provide a real-life case study to illustrate your points.

---

**Section D: Practical Application**

**Question 7: Technology and Society**  
*(10 Points)*

Evaluate the impact of artificial intelligence on the job market. Discuss how AI could both positively and negatively affect employment rates. Propose three strategies to mitigate any adverse effects on the workforce.

---

**Question 8: Environmental Science**  
*(10 Points)*

Climate change poses a significant threat to global biodiversity. Choose a specific ecosystem (e.g., coral reefs, tropical rainforests) and discuss how climate change affects its flora and fauna. Suggest practical measures to protect and preserve this ecosystem from further damage.

---

**End of Examination**

**Please ensure you have answered all parts of every question. Review your solutions carefully before submission.**

---

**Note:** This test assumes a high level of interdisciplinary knowledge, analytical skill, and critical thinking, in line with a difficulty rating of 7.
\end{document}
