
\documentclass{article}
\usepackage{amsmath}
\begin{document}
Certainly! Below is a sample test that aligns with a difficulty level of 7, formatted to reflect a college-level Northwestern University exam style. The test includes a variety of question types to challenge students at an upper-undergraduate level. 

---

**Northwestern University**

**Department of [Subject]**

**Course Number: [Course Title]**

**Midterm Exam**

**Instructions:**
- Duration: 2 hours
- Answer all questions clearly and concisely.
- Show all workings for questions involving calculations.
- Write all answers in the space provided.
- No electronic devices are allowed.

**Student Name: ___________________**
**Student ID: ______________________**

---

**Section A: Short Answer and Calculation**

1. **(15 points)** Describe the primary differences between intrinsic and extrinsic semiconductor materials. How do these differences impact their electrical conductivity?

---

2. **(15 points)** A protein folds spontaneously at room temperature. Using the concept of Gibbs free energy, explain why this folding occurs, considering both enthalpy and entropy changes.

---

3. **(10 points)** Solve the integral: \(\int_{0}^{\pi} \sin(x) \cos(x) \, dx\).

---

**Section B: Multiple Choice**

4. **(10 points)** Which of the following compounds has the highest boiling point?
   
    a) Methane
   
    b) Ethanol
   
    c) Carbon dioxide
   
    d) Water

---

5. **(10 points)** In the context of financial economics, which of the following statements is true about the efficient market hypothesis?

    a) All investors have equal access to information and act rationally.
    
    b) Stock prices always reflect all available information.
    
    c) Markets can be beaten with advanced, proprietary algorithms.
    
    d) Insider information can predict market movements.

---

**Section C: Essay**

6. **(20 points)** Discuss the role of Photosystem II in the light-dependent reactions of photosynthesis. How does the process of photolysis contribute to the production of oxygen and ATP?

---

**Section D: Data Analysis**

7. **(10 points)** You are given the following data points for temperature (°C) vs. solubility (g/L) of a solute: 

| Temperature (°C) | Solubility (g/L) |
|------------------|------------------|
| 20               | 50               |
| 30               | 55               |
| 40               | 60               |
| 50               | 70               |

Using the data provided, plot the solubility vs. temperature on a graph. From the graph, estimate the solubility at 45°C.

---

**Section E: Proof and Reasoning**

8. **(10 points)** Prove that the sequence defined by \(a_n = \frac{1}{n}\) converges to 0 as \(n \to \infty\).

---

**TOTAL: 100 points**

---

**End of Exam**

Please check your answers before submitting. Good luck!
\end{document}
